Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-10 csf-2017/paper.tex
grammar

Already important is the fact that the return pointer must be provided to the
adversary as a local capability. If not, the adversary would be able to store
away the return pointer in a global data structure, and he would be able to jump
to it in circumstances where this should not be possible: for example, he may
store the return pointer, legally jump to it a first time, wait to be invoked
again and then jump to the old return pointer a second time, rather than the new
return pointer received for the new invocation. Similarly, he may store the
return pointer, invoke a function in our code, wait for us to invoke him again
and then jump to the stored, old return pointer rather than the new one he
received upon the second invocation. \lau{If we need space, then maybe one of the examples is sufficient.}

@@

\textbf{Invoking an adversary callback} If we have a higher-order interface to
the adversary, we might need to invoke an adversary callback. In this case, not
so much changes with respect to the situation where we invoke regular adversary
code. The adversary can provide a callback as a capability for us to jump to,
either an $\entry$-capability if he wants to protect himself from us or just an
$\exec$ capability if they is not worried about that. However, there is one
scenario that we need to prevent, namely that they constructs the callback
capability to point into the stack, where they may have stored local
capabilities that he should not have access to upon invocation of the callback.
Specifically, he might store return pointers and stack pointers from previous
stack frames there, and illegally use them inside the callback.

@@

Our answer is that the adversary should provide it to us, much like we provide
him with a current stack pointer when we invoke his code.  However, it is
important that we do not just accept any capability as a stack pointer but check
that it is safe to use.  Specifically, we check that it is indeed a $\rwlx$
pointer and that its current address points just below its start address.
Without these checks, err...
\dominique{is this needed for security or just for convenience?}
\lau{Say we are called with a stack capability that is global and $\rwx$ as well as an integer as a non-local return pointer (this is fair game as the adversary has to follow no rules). Now you push the l(a)unch codes to what you think is the stack and \texttt{scall} the callback. At this point \texttt{scall} does its thing, but because it never attempts to store anything local it will succeed and jump to the adversary! The adversary can now look at what you thought was the stack and eat your lunch or fire the missiles as they prefer. It is not sufficient to require the stack to be just local because there may be a global equivalent. We know this is not the case for the rwlx capability because we have a system wide assumption that all rwlx capabilities are local.
Finally the adjustment of the pointer in \texttt{prepstck} (or whatever I called it) is a convenience/ space efficiency thing purely.}

>>>>

Already important is the fact that the return pointer must be provided to the
adversary as a local capability. If not, the adversary would be able to store
away the return pointer in a global data structure, and they would be able to jump
to it in circumstances where this should not be possible: for example, they may
store the return pointer, legally jump to it a first time, wait to be invoked
again and then jump to the old return pointer a second time, rather than the new
return pointer received for the new invocation. Similarly, they may store the
return pointer, invoke a function in our code, wait for us to invoke him again
and then jump to the stored, old return pointer rather than the new one he
received upon the second invocation. \lau{If we need space, then maybe one of the examples is sufficient.}

@@

\textbf{Invoking an adversary callback} If we have a higher-order interface to
the adversary, we might need to invoke an adversary callback. In this case, not
so much changes with respect to the situation where we invoke regular adversary
code. The adversary can provide a callback as a capability for us to jump to,
either an $\entry$-capability if they want to protect themselves from us or just an
$\exec$ capability if they are not worried about that. However, there is one
scenario that we need to prevent, namely that they construct the callback
capability to point into the stack, where they may have stored local
capabilities that they should not have access to upon invocation of the callback.
Specifically, they might store return pointers and stack pointers from previous
stack frames there, and illegally use them inside the callback.

@@

Our answer is that the adversary should provide it to us, much like we provide
them with a current stack pointer when we invoke his code.  However, it is
important that we do not just accept any capability as a stack pointer but check
that it is safe to use.  Specifically, we check that it is indeed a $\rwlx$
pointer and that its current address points just below its start address.
Without these checks, err...
\dominique{is this needed for security or just for convenience?}
\lau{Say we are called with a stack capability that is global and $\rwx$ as well as an integer as a non-local return pointer (this is fair game as the adversary has to follow no rules). Now you push the l(a)unch codes to what you think is the stack and \texttt{scall} the callback. At this point \texttt{scall} does its thing, but because it never attempts to store anything local it will succeed and jump to the adversary! The adversary can now look at what you thought was the stack and eat your lunch or fire the missiles as they prefer. It is not sufficient to require the stack to be just local because there may be a global equivalent. We know this is not the case for the rwlx capability because we have a system wide assumption that all rwlx capabilities are local.
Finally the adjustment of the pointer in \texttt{prepstck} (or whatever I called it) is a convenience/ space efficiency thing purely.}
